Supplemental Materials, Methods and Results

### 2021-05-04 supp.Rmd
Updated supplement with new fancy tables. Took a bit, but should be now easy to modify styles to suite what we need for all the contrast tables

  # Fit model for linear hypothesis tests
    Predator$PopBRInt <- interaction(Predator$Population,Predator$Predator, Predator$BodyRegion)
     PredatorAC2 <- lmer(dS ~ -1 + PopBRInt + (1|ID), data=Predator)
     summary(PredatorAC2)

 # Contrasts hypothesis tests, but use RVE 
                 result5 <- Wald_test(PredatorAC2, constraints = constrain_pairwise(c(2:9)), vcov="CR2", tidy = TRUE)
    result5$p_val_bonfer <- sapply(p.adjust(result5$p_val, "bonferroni"), function(x) p_value(x))

##########
## Chromatic Contrast - dL
########

@@

 # Contrasts hypothesis tests, but use RVE 
                 result6 <- Wald_test(PredatorCC2, constraints = constrain_pairwise(c(2:9), with_zero = TRUE), vcov="CR2", tidy = TRUE)
    result6$p_val_bonfer <- sapply(p.adjust(result6$p_val, "bonferroni"), function(x) p_value(x))

@@

```{r tableS1}
summary(result1)
```

>>>>

  # Fit model for linear hypothesis tests
    Predator$PopBRInt <- interaction(Predator$Population,Predator$Predator, Predator$BodyRegion)
     PredatorAC2 <- lmer(dL ~ -1 + PopBRInt + (1|ID), data=Predator)
     summary(PredatorAC2)

 # Contrasts hypothesis tests, but use RVE 
                 result5 <- Wald_test(PredatorAC2, constraints = constrain_pairwise(c(1:16)), vcov="CR2", tidy = TRUE)
 string <- c("PopBRIntKenya.snake.midflank - PopBRIntHawaii.snake.midflank|PopBRIntKenya.snake.gular - PopBRIntHawaii.snake.gular|PopBRIntKenya.snake.tailbase - PopBRIntHawaii.snake.tailbase|PopBRIntKenya.snake.topflank - PopBRIntHawaii.snake.topflank|PopBRIntKenya.bird.midflank - PopBRIntHawaii.bird.midflank|PopBRIntKenya.bird.gular - PopBRIntHawaii.bird.gular|PopBRIntKenya.bird.tailbase - PopBRIntHawaii.bird.tailbase|PopBRIntKenya.bird.topflank - PopBRIntHawaii.bird.topflank")
    result5 <- result5[grep(string, result5$hypothesis),]
    result5$p_val_bonfer <- sapply(p.adjust(result5$p_val, "bonferroni"), function(x) p_value(x))

##########
## Chromatic Contrast - dS
########

@@

 # Contrasts hypothesis tests, but use RVE 
                 result6 <- Wald_test(PredatorCC2, constraints = constrain_pairwise(c(1:16), with_zero = TRUE), vcov="CR2", tidy = TRUE)
                   string <- c("PopBRIntKenya.snake.midflank - PopBRIntHawaii.snake.midflank|PopBRIntKenya.snake.gular - PopBRIntHawaii.snake.gular|PopBRIntKenya.snake.tailbase - PopBRIntHawaii.snake.tailbase|PopBRIntKenya.snake.topflank - PopBRIntHawaii.snake.topflank|PopBRIntKenya.bird.midflank - PopBRIntHawaii.bird.midflank|PopBRIntKenya.bird.gular - PopBRIntHawaii.bird.gular|PopBRIntKenya.bird.tailbase - PopBRIntHawaii.bird.tailbase|PopBRIntKenya.bird.topflank - PopBRIntHawaii.bird.topflank")
    result6 <- result6[grep(string, result6$hypothesis),]
    result6$p_val_bonfer <- sapply(p.adjust(result6$p_val, "bonferroni"), function(x) p_value(x))

@@

### Changes in visual signals across body regions show similar patterns
We took measurements of spectral reflectance for different body regions of each chamaleon. In our primary analysis, we averaged across these different body regions because we were interested only in whether visual signals were different in Kenya and Hawaii overall. This was justified given that, across the different body regions, effects were largely in a similar direction, and often of similar magnitude (Figure \@ref(fig:FigS1) and Table \@ref(tab:tableS1)).

```{r tableS1, tab.cap = "Pairwise comparisons of achormatic contrast between Kenyan and Hawaiian chameleon displays to a snake and bird visual system. Four different body regions ('gular', 'midflank', 'tailbase', topflank') are provided along with pairwise Wald test for contrast significance. Wald test uses a robust variance correction on the standard errors."}

# Split snakes and birds
result5_snake <-  result5[grep("snake", result5$hypothesis), ] %>% mutate(Species = c("Snake", rep("",3)))
 result5_bird <- result5[grep("bird", result5$hypothesis), ] %>% mutate(Species = c("Bird", rep("",3)))

 # Bind together in order
  final_r5 <- rbind(result5_snake,result5_bird)

  # Clean
  final_r5 <- final_r5 %>% 
              select(-test, -delta, -df_num) %>%
              mutate(hypothesis = gsub("PopBRInt", "", hypothesis)) %>%
              select(Species, hypothesis, Fstat, df_denom, p_val, p_val_bonfer)

table_style <- function(table){
    table <- table %>% width(j = 1, width = 1) %>% width(j = 2, width = 2.5) %>% 
             align(align = "center", part = "header") %>% 
              align(i = 1:8, j = 1:6, align = "center", part = "body") %>% 
            compose(part = "header", j = 1, value = as_paragraph(as_b("Predator"))) %>% 
             compose( part = "header", j = 2, value = as_paragraph(as_b("Contrast"))) %>% 
            compose(part = "header", j = 3, value = as_paragraph(as_b("F"))) %>%
            compose(part = "header", j = 4, value = as_paragraph(as_b("DF"))) %>% 
            compose(part = "header", j = 5, value = as_paragraph(as_b("p"))) %>% 
            compose(part = "header", j = 6, value = as_paragraph(as_b("p"), as_sub(as_b("Bonferroni")))) %>%
            compose(part = "body", i = 1, j = 2, 
                    value = as_paragraph("Kenya", as_sub("gular"), " - ", "Hawaii", as_sub("gular")))  %>% 
            compose(part = "body", i = 2, j = 2, 
                    value = as_paragraph("Kenya", as_sub("midflank"), " - ", "Hawaii", as_sub("midflank"))) %>% 
            compose(part = "body", i = 3, j = 2, 
                    value = as_paragraph("Kenya", as_sub("tailbase"), " - ", "Hawaii", as_sub("tailbase"))) %>% 
            compose(part = "body", i = 4, j = 2, 
                    value = as_paragraph("Kenya", as_sub("topflank"), " - ", "Hawaii", as_sub("topflank"))) %>% 
            compose(part = "body", i = 5, j = 2, 
                    value = as_paragraph("Kenya", as_sub("gular"), " - ", "Hawaii", as_sub("gular")))  %>% 
            compose(part = "body", i = 6, j = 2, 
                    value = as_paragraph("Kenya", as_sub("midflank"), " - ", "Hawaii", as_sub("midflank"))) %>% 
            compose(part = "body", i = 7, j = 2, 
                    value = as_paragraph("Kenya", as_sub("tailbase"), " - ", "Hawaii", as_sub("tailbase"))) %>% 
            compose(part = "body", i = 8, j = 2, 
                    value = as_paragraph("Kenya", as_sub("topflank"), " - ", "Hawaii", as_sub("topflank")))
 return(table)
}

ft5 <- flextable(final_r5) %>%
        table_style(.) %>% 
        add_header_row(values = "Achromatic Contrast", colwidths = 6)

 ft5

```{r tableS2, tab.cap = "Pairwise comparisons of achormatic contrast between Kenyan and Hawaiian chameleon displays to a snake and bird visual system. Four different body regions ('gular', 'midflank', 'tailbase', topflank') are provided along with pairwise Wald test for contrast significance. Wald test uses a robust variance correction on the standard errors."}

# Split snakes and birds

result6_snake <- result6[grep("snake", result6$hypothesis), ] %>% mutate(Species = c("Snake", rep("",3)))
 result6_bird <- result6[grep("bird", result6$hypothesis), ] %>% mutate(Species = c("Bird", rep("",3)))

# Bind together in order
 final_r6 <- rbind(result6_snake,result6_bird)

# Clean
 final_r6 <- final_r6 %>% 
              select(-test, -delta, -df_num) %>%
              mutate(hypothesis = gsub("PopBRInt", "", hypothesis)) %>%
              select(Species, hypothesis, Fstat, df_denom, p_val, p_val_bonfer)

 # Table
 ft6 <- flextable(final_r6) %>%
        table_style(.) %>% 
        add_header_row(values = "Chromatic Contrast", colwidths = 6)

 ft6
```
